PyQBench: a Python library for benchmarking gate-based quantum computers

### 2023-03-05 txt/manuscript.tex
add impact

\section{Impact}
\todo[inline]{OJCIEC WYKAZ SIE, bo trzeba to dobrze sprzedac, nizej tekst z formatki softwarex co powinna zawierac ta sekcja}
This software has two main contributions.

\textbf{This is the main section of the article and the reviewers weight the
description here appropriately}

Indicate in what way new research questions can be pursued as a result of the
software (if any).

Indicate in what way, and to what extent, the pursuit of existing research
questions is improved (if so).

Indicate in what way the software has changed the daily practice of its users
(if so).

Indicate how widespread the use of the software is within and outside the
intended user group.

Indicate in what way the software is used in commercial settings and/or how it
led to the creation of spin-off companies (if so).

>>>>

\section{Impact}
With the surge of availability of quantum computing architectures in recent
years it becomes increasingly difficult to keep track of their relative
performance. To make this case even more difficult, various providers give
access to different figures of merit for their architectures. Our package allows
the user to test various architectures, available through \texttt{qiskit} and
Amazon BraKet using problems with simple operational interpretation. We provide
one example built-in in the package. Furthermore, we provide a powerful tool for
the users to extend the range of available problems in a way that suits their
needs.

Due to this possibility of extension, the users are able to test specific
aspects of their architecture of interest. For example, if their problem is
related to the amount of coherence (the sum of absolute value of off-diagonal
elements) of the states present during computation, they are able to quickly
prepare a custom experiment, launch it on desired architectures, gather the
result, based on which they can decide which specific architecture they should
use.

Finally, we provide the source code of PyQBench on GitHub~\cite{} under on open
source license which will allow users to utilize and extend our package in their
specific applications.
